---
title: "2024_processing"
author: "Keleigh Reynolds"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(skimr)
library(janitor)
library(tidyverse)
library(dplyr)
```

First bring in the raw data

```{r}
raw<-read.csv(here::here("data/Copy of Bacteria_Data_MRBP_for_Database_2024.csv"))
```

Now we'll subset to the columns we need for the DB
```{r}
temp_result<-raw %>% 
  select(c("sample_date",
           "SITE_ID",
           "sys_sample_code",
           "lab_sdg",
           "lab_anl_method_name",
           "analysis_date",
           "fraction",
           "column_number",
           "test_type",
           "lab_matrix_code",
           "analysis_location",
           "basis",
           "container_id",
           "dilution_factor",
           "prep_method",
           "prep_date",
           "leachate_method",
           "leachate_date",
           "lab_name_code",
           "qc_level",
           "lab_sample_id",
           "percent_moisture",
           "subsample_amount",
           "subsample_amount_unit",
           "analyst_name",
           "instrument_id",
           "preservative",
           "final_volume",
           "final_volume_unit",
           "cas_rn",
           "chemical_name",
           "result_value",
           "result_error_delta",
           "result_type_code",
           "reportable_result",
           "detect_flag",
           "lab_qualifiers",
           "validator_qualifiers",
           "interpreted_qualifiers",
           "validated_yn",
           "method_detection_limit",
           "reporting_detection_limit",
           "quantitation_limit",
           "result_unit",
           "detection_limit_unit",
           "tic_retention_time",
           "minimum_detectable_conc",
           "counting_error",
           "uncertainty",
           "critical_value",
           "validation_level",
           "result_comment",
           "qc_original_conc",
           "qc_spike_added",
           "qc_spike_measured",
           "qc_spike_recovery",
           "qc_dup_original_conc",
           "qc_dup_spike_added",
           "qc_dup_spike_measured",
           "qc_dup_spike_recovery",
           "qc_rpd","qc_spike_lcl",
           "qc_spike_ucl",
           "qc_rpd_cl",
           "qc_spike_status",
           "qc_dup_spike_status",
           "qc_rpd_status"))
                          

temp_sample <- raw %>% 
  select(c(SITE_ID,SITE_ID_CORR_IND,SEIH_EVENT_SMAS_HISTORY_ID,DEC_sample_type,
           "data_provider",
           "sys_sample_code",
           "sample_name",
           "sample_matrix_code",
           "sample_type_code",
           "sample_source",
           "parent_sample_code",
           "sample_delivery_group",
           "sample_date",
           "sys_loc_code",
           "start_depth",
           "end_depth",
           "depth_unit",
           "chain_of_custody",
           "sent_to_lab_date",
           "sample_receipt_date",
           "sampler",
           "sampling_company_code",
           "sampling_reason",
           "sampling_technique",
           "task_code",
           "collection_quarter",
           "composite_yn",
           "composite_desc",
           "sample_class",
           "custom_field_1",
           "custom_field_2",
           "custom_field_3",
           "lat",
           "long"))



```

```{r}
temp_sample$lab_sdg<-temp_sample$sample_delivery_group
temp_sample<-temp_sample %>% 
  distinct()

```

Test join by sys_sample_code and SDG
```{r Initial join test}
test_join_sample.result <- left_join(temp_sample, temp_result, by = c("sys_sample_code", "lab_sdg"))

# CHECKS OUT OKAY. Same number of records created in joined table as in RESULT table.

rm(test_join_sample.result)

#fix fecal coliform

#fix the fecal coliform names
temp_result<-temp_result %>% 
  mutate(chemical_name=case_when(
    chemical_name %in% "COLIFORM, FECAL"~"coliform, fecal",
    TRUE~chemical_name
  ),
  sample_delivery_group = lab_sdg)

#fix the estimated units- no < or > signs allowed
result.all<-temp_result %>% 
  mutate(validator_qualifiers = case_when(
    result_value == "<1"~"J",
    result_value == ">2,419.6"~"J",
    TRUE~ "A"),
    result_value = case_when(
    result_value == "<1"~"1",
    result_value == ">2,419.6"~"2419.6",
    result_value == ">2419.6"~"2419.6",
    TRUE~result_value),
    result_value= as.numeric(result_value),
    fraction = ""
  )

```

Join flags and related fields to results table
```{r Join QAQC flags}
result.all <- result.all %>% 
  mutate(chemical_name = tolower(chemical_name))

result.all$fraction<-tolower(result.all$fraction)
result.all<-result.all %>% 
  select(sys_sample_code,sample_delivery_group,chemical_name,fraction,everything())


#  Look for duplicate records (possible issues with join)
dups <- result.all %>% 
  group_by(sys_sample_code, sample_delivery_group, chemical_name, fraction) %>% 
  mutate(dups = n()) %>% 
  filter(dups > 1)
 # Found: nothing for bacteria
```

Flag any field results not run through QAQC
```{r Populated flags fir non-QAQCd data}
# Join sample type field from SAMPLE table to gather required info for filtering
sample.all.type <- temp_sample %>% 
  select(SITE_ID, sys_sample_code, sample_source, sample_delivery_group, DEC_sample_type, sample_type_code)

result.all.type <- left_join(result.all, sample.all.type, by = c("sys_sample_code", "sample_delivery_group")) 
  # select(SITE_ID, sample_source, DEC_sample_type, sample_type_code, validator_qualifiers, VALIDATOR_QUAL_EXPLN, everything())

# Check this to see what types of samples got flags. Only N and N_xxx samples should be getting flags.
result.all.type.check <- result.all.type %>% 
  select(validator_qualifiers, DEC_sample_type) %>% 
  distinct()

# Filter out normal samples that didn't get flags to verify that only the ones intentionally not flagged are there.
result.all.notflagged.n <- result.all.type %>% 
  filter(is.na(validator_qualifiers),
         DEC_sample_type %in% "N",
         sample_source %in% "Field")
unique(result.all.notflagged.n$SITE_ID)
# Found: nothing!

# Mark validated_yn as "N" for normal field samples with no validator flag. Add E flags and explanations if needed.
result.all.flagged2 <- result.all.type %>% 
  mutate(validated_yn = ifelse(
    is.na(validator_qualifiers) &
      DEC_sample_type %in% "N" &
      sample_source %in% "Field",
    "N", validated_yn)) 


# Verify that only remaining field "N" samples without flags are those params we don't flag
result.all.flagged2.naflags <- result.all.flagged2 %>% 
  filter(is.na(validator_qualifiers),
         sample_source %in% "Field",
         DEC_sample_type %in% "N")
# Triple check. Ignore me. Above checks out :)

#clean up the workspace
rm(sample.all.type, result.all.type, result.all.type.check, result.all.notflagged.n, result.all.flagged2.naflags,dups,result.all.flagged2)


```


Reformat field names for WQMA format

```{r Reformat field names}
sample.all<-temp_sample %>% 
  mutate(SITE_ID_CORR_IND = "") %>% 
  #fix the dup/fb on the sites
  mutate(SEIH_EVENT_SMAS_HISTORY_ID = SITE_ID,#keep a record of these
         SITE_ID = gsub("*-DUP","",SITE_ID),
         SITE_ID = gsub("*-FB","",SITE_ID))

sample.all.formatted <- sample.all %>%
  filter(!grepl("*-DUP",SEIH_EVENT_SMAS_HISTORY_ID)) %>% 
  filter(!grepl("*-FB",SEIH_EVENT_SMAS_HISTORY_ID)) %>% 
  mutate(sample_date = as.POSIXct(sample_date,format = "%m/%d/%Y %H:%M"),
         EVENT_ID = paste(SITE_ID,
                          "_",
                          format(sample_date,"%Y%m%d"),
                          "T",
                          format(sample_date,"%H%M"),
                          sep = "")) %>% 
  select(EVENT_ID,everything()) %>% 
  mutate(REPLICATE = 1,
         SAMPLE_CREW = "MRBP Volunteers",
         SAMPLE_LOCATION = "waded",
         SAMPLE_METHOD_DESCRIPTION = "grab",
         SAMPLE_METHOD_REFERENCE = "WQM-0072_V24-1_Mohawk-Bacteria",
         SAMPLE_TYPE = "water_column",
         SAMPLE_COMMENT = "",
         SAMPLE_DEPTH_METERS = 0.1) %>% #add missing ones
  select(
    SITE_ID,
    EVENT_ID,
    SAMPLE_DELIVERY_GROUP = lab_sdg,
    SAMPLE_LAB = sampling_company_code,
    SAMPLE_METHOD = sampling_technique,
    SAMPLE_NAME = sample_name,
    SAMPLE_ORGANIZATION = sampling_company_code,
    SAMPLE_SOURCE = data_provider,
    # SAMPLE_ID - did not create this one as it's created in the db itself? FK?
    SAMPLE_LATITUDE = lat,
    SAMPLE_LONGITUDE = long,
    SAMPLE_DELIVERY_GROUP = lab_sdg,
    REPLICATE,
    SAMPLE_CREW,
    SAMPLE_LOCATION,
    SAMPLE_METHOD_DESCRIPTION,
    SAMPLE_METHOD_REFERENCE,
    SAMPLE_TYPE,
    SAMPLE_COMMENT,
    SAMPLE_DEPTH_METERS)


result.all.formatted <- result.all %>%
  mutate(SEIH_EVENT_SMAS_HISTORY_ID = SITE_ID,#keep a record of these
         SITE_ID = gsub("*-DUP","",SITE_ID),
         SITE_ID = gsub("*-FB","",SITE_ID)) %>% 
  filter(!grepl("*-DUP",SEIH_EVENT_SMAS_HISTORY_ID)) %>% 
  filter(!grepl("*-FB",SEIH_EVENT_SMAS_HISTORY_ID)) %>% 
                #remove the qc stuff
  mutate(sample_date = as.POSIXct(sample_date,format = "%m/%d/%Y %H:%M"),tz = "America/New_York") %>% #first fix teh date
  mutate(EVENT_ID = paste(SITE_ID,
                          "_",
                          format(sample_date,"%Y%m%d"),
                          "T",
                          format(sample_date,"%H%M"),
                          sep = ""),
         ANALYSIS_DATETIME = as.Date(analysis_date,format("%m/%d/%Y")),
         DETECT_FLAG = case_when(
           lab_qualifiers %in% ">"~"greater_than",
           lab_qualifiers %in% "<" ~ "less_than",
           TRUE ~ ""
         ),
         DETECTION_LIMIT_UNIT = "cfu/100mL",
         LAB_VALIDATION_LEVEL = "quant",
         PREP_METHOD = "not_applicable",
         QUALIFIER_SOURCE = "laboratory",
         REPORTABLE_RESULT = "Yes",
         RESULT_CATEGORY = "not_applicable",
         RESULT_COMMENT ="",
         RESULT_QUALIFIER_NOTE = DETECT_FLAG, #this one seemed to match
         RESULT_TYPE_CODE = "TRG",
         TEST_TYPE = "initial",
         RESULT_QUALIFIER_DESCRIPTION = 
           case_when(validator_qualifiers %in% "A"~"accepted",
                     validator_qualifiers %in% "J" ~ "Estimated concentration - still suitable for most data uses",
                     TRUE ~ "error"
                     
           ),
         PARAMETER_NAME = case_when(
           chemical_name %in% "e. coli" ~ "e_coli",
           chemical_name %in% "coliform, fecal" ~"fecal_coliform",
           TRUE ~ "error"),
         FRACTION = "not_applicable",
         CASRN = cas_rn,
         MATRIX = "water",
         METHOD_SPECIATION = "not_applicable") %>% 
  select(
    SITE_ID,
    EVENT_ID,
    PARAMETER_NAME,
    FRACTION,
    CASRN,
    MATRIX,
    METHOD_SPECIATION,
    DILUTION_FACTOR = dilution_factor,
    FINAL_VOLUME = final_volume,
    FINAL_VOLUME_UNIT = final_volume_unit,
    LAB_ANALYTICAL_METHOD = lab_anl_method_name,
    LAB_QUALIFIER = lab_qualifiers,
    LAB_SAMPLE_ID = sys_sample_code,
    METHOD_DETECTION_LIMIT = method_detection_limit,
    PREP_DATETIME = analysis_date,
    QUANTITATION_LIMIT = quantitation_limit,
    REPORTING_DETECTION_LIMIT = reporting_detection_limit,
    RESULT_QUALIFIER = validator_qualifiers,
    RESULT_VALUE = result_value,
    SUBSAMPLE_AMOUNT = subsample_amount,
    SUBSAMPLE_AMOUNT_UNIT = subsample_amount_unit,
    #PARAMETER_ID = i did not do this one since it looks like its uniquely created through the db
    #RESULT_ID = same, PK
    #SAMPLE_ID - same FK
    RESULT_QUALIFIER = validator_qualifiers,
    ANALYSIS_DATETIME,
    DETECTION_LIMIT_UNIT,
    LAB_VALIDATION_LEVEL,
    PREP_METHOD,
    QUALIFIER_SOURCE,
    REPORTABLE_RESULT,
    RESULT_CATEGORY,
    RESULT_COMMENT,
    RESULT_QUALIFIER_NOTE, #this one seemed to match
    RESULT_TYPE_CODE,
    TEST_TYPE,
    RESULT_QUALIFIER_DESCRIPTION)


```
 
subset the quality control samples 

```{r}

qa <-c("*-DUP","*-FB") #listing the qa types

qa_df<-result.all %>% 
  mutate(SEIH_EVENT_SMAS_HISTORY_ID = SITE_ID,#keep a record of these
         SITE_ID = gsub("*-DUP","",SITE_ID),
         SITE_ID = gsub("*-FB","",SITE_ID)) %>% 
  filter(grepl(paste(qa,collapse = "|"),SEIH_EVENT_SMAS_HISTORY_ID)) %>%   #subset to qa stuff
  mutate(sample_date = as.POSIXct(sample_date,format = "%m/%d/%Y %H:%M")) %>% #fix the date
  mutate(EVENT_ID = paste(SITE_ID,format(sample_date,"%Y%m%d"),
                          "T",
                          format(sample_date,"%H%M"),
                          sep = ""),
         ANALYSIS_DATETIME = as.Date(analysis_date,format("%m/%d/%Y")),
         DETECT_FLAG = case_when(
           lab_qualifiers %in% ">"~"greater_than",
           lab_qualifiers %in% "<" ~ "less_than",
           TRUE ~ ""
         ),
         DETECTION_LIMIT_UNIT = "cfu/100mL",
         LAB_VALIDATION_LEVEL = "quant",
         PREP_METHOD = "not_applicable",
         QUALIFIER_SOURCE = "laboratory",
         REPORTABLE_RESULT = "Yes",
         RESULT_CATEGORY = "not_applicable",
         RESULT_COMMENT ="",
         RESULT_QUALIFIER_NOTE = DETECT_FLAG, #this one seemed to match
         RESULT_TYPE_CODE = "TRG",
         TEST_TYPE = "initial",
         RESULT_QUALIFIER_DESCRIPTION = 
           case_when(validator_qualifiers %in% "A"~"accepted",
                     validator_qualifiers %in% "J" ~ "Estimated concentration - still suitable for most data uses",
                     TRUE ~ "error"
                     
           ),
         PARAMETER_NAME = case_when(
           chemical_name %in% "e. coli" ~ "e_coli",
           chemical_name %in% "coliform, fecal" ~"fecal_coliform",
           TRUE ~ "error"),
         FRACTION = "not_applicable",
         CASRN = cas_rn,
         SAMPLE_SOURCE = "lab",
         SAMPLE_TYPE = "chemistry_qc",
         MATRIX = "water",
         METHOD_SPECIATION = "not_applicable",
         SAMPLE_DELIVERY_GROUP = sample_delivery_group) %>% 
  select(
    SITE_ID,
    EVENT_ID,
    SAMPLE_DELIVERY_GROUP,
    PARAMETER_NAME,
    FRACTION,
    CASRN,
    MATRIX,
    METHOD_SPECIATION,
    DILUTION_FACTOR = dilution_factor,
    FINAL_VOLUME = final_volume,
    FINAL_VOLUME_UNIT = final_volume_unit,
    LAB_ANALYTICAL_METHOD = lab_anl_method_name,
    LAB_QUALIFIER = lab_qualifiers,
    LAB_SAMPLE_ID = sys_sample_code,
    METHOD_DETECTION_LIMIT = method_detection_limit,
    PREP_DATETIME = analysis_date,
    QUANTITATION_LIMIT = quantitation_limit,
    REPORTING_DETECTION_LIMIT = reporting_detection_limit,
    RESULT_QUALIFIER = validator_qualifiers,
    RESULT_VALUE = result_value,
    SAMPLE_NAME = SEIH_EVENT_SMAS_HISTORY_ID,
    SAMPLE_SOURCE,
    SAMPLE_TYPE,
    SUBSAMPLE_AMOUNT = subsample_amount,
    SUBSAMPLE_AMOUNT_UNIT = subsample_amount_unit,
    #PARAMETER_ID = i did not do this one since it looks like its uniquely created through the db
    #RESULT_ID = same, PK
    #SAMPLE_ID - same FK
    RESULT_QUALIFIER = validator_qualifiers,
    ANALYSIS_DATETIME,
    DETECTION_LIMIT_UNIT,
    LAB_VALIDATION_LEVEL,
    PREP_METHOD,
    QUALIFIER_SOURCE,
    REPORTABLE_RESULT,
    RESULT_CATEGORY,
    RESULT_COMMENT,
    RESULT_QUALIFIER_NOTE, #this one seemed to match
    RESULT_TYPE_CODE,
    TEST_TYPE,
    RESULT_QUALIFIER_DESCRIPTION,
    #QUALITY_CONTROL_ID = #assigned by db
    QC_DUP_ORIGINAL_CONCENTRATION = qc_dup_original_conc,
    QC_DUP_SPIKE_ADDED =  qc_dup_spike_added,
    QC_DUP_SPIKE_MEASURED = qc_dup_spike_measured,
    QC_DUP_SPIKE_RECOVERY = qc_dup_spike_recovery,
    QC_DUP_SPIKE_STATUS = qc_dup_spike_status,
    QC_LEVEL = qc_level,
    QC_ORIGINAL_CONCENTRATION = qc_original_conc,
    QC_RPD = qc_rpd,
    QC_RPD_CL = qc_rpd_cl,
    QC_RPD_STATUS = qc_rpd_status,
    QC_SPIKE_ADDED = qc_spike_added,
    QC_SPIKE_LCL = qc_spike_lcl,
    QC_SPIKE_MEASURED = qc_spike_measured,
    QC_SPIKE_RECOVERY = qc_spike_recovery,
    QC_SPIKE_STATUS = qc_spike_status,
    QC_SPIKE_UCL = qc_spike_ucl
  )
    
  skimr::skim(qa_df)  


```

Now we just need to make sure they are all good, matching and the like. RPD's were calculated using geomeans

```{r check-site-ids}
#read in charlie's 23 and 24 site correction files
# s23<-readxl::read_excel("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/siteIdCrosswalkTable2023_v1.xlsx")

s24<-readxl::read_excel("L:/DOW/BWAM Share/data/data_warehouse_staging/2024_V3/raw_data/stream/siteIdCrosswalkTable2024_v4.xlsx")


#read in the existing sites in the wqma table
wqma<-read.csv(here::here("outputs/sites_table_wqma.csv"))
#take out project since that will create extra joins
wqma<-wqma %>% 
  select(-c("PROJECT","WIPWL")) %>% 
  distinct()

sites_bacteria <- sample.all.formatted %>% 
  select(SITE_CODE = SITE_ID,
         EVENT_ID) %>% 
  distinct()
#looks like these are all 2024

wqma_join<-left_join(sites_bacteria,wqma,
                     by = "SITE_CODE")
#filter out the ones that are missing
missing_bacteria_sites<-wqma_join %>% 
  filter(is.na(LATITUDE)) %>% 
  select(SITE_CODE) %>% 
  distinct()

#rejoin with the raw for the lat/longs of the sites
raw_site_lat<-raw %>% 
  select(SITE_ID,lat,long) %>% 
  filter(SITE_ID %in% missing_bacteria_sites$SITE_CODE) %>% 
  distinct()

#write to file for the team to put together
# write.csv(raw_site_lat,
#           "outputs/missing_bacteria_sites.csv")

```


```{r checking that the column types are correct}

build_dir <- file.path(
  "L:",
  "DOW",
  "BWAM Share",
  "data",
  "parquet",
  "build_tables")


result_df <- arrow::open_dataset(sources = file.path(build_dir, "RESULT.parquet")) |> 
  filter(LAB_SAMPLE_ID %in% "R1202229-011") %>% #trying to limit it so the collection isnt crazy
  distinct() %>% 
  collect()



check<-janitor::compare_df_cols(result_df, 
                         result.all.formatted, 
                         return = "mismatch")

result.all.formatted2<-result.all.formatted %>% 
  mutate(ANALYSIS_DATETIME = as.POSIXct(as.Date(ANALYSIS_DATETIME,"%Y-%m-%d"),
                                        tz = "America/New_York"),
         DILUTION_FACTOR = as.numeric(DILUTION_FACTOR),
         FINAL_VOLUME = as.numeric(FINAL_VOLUME),
         METHOD_DETECTION_LIMIT = as.numeric(METHOD_DETECTION_LIMIT),
         PREP_DATETIME = as.POSIXct(as.Date(PREP_DATETIME,"%m/%d/%Y"),
                                    tz = "America/New_York"),
         QUANTITATION_LIMIT = as.numeric(QUANTITATION_LIMIT),
         SUBSAMPLE_AMOUNT = as.numeric(SUBSAMPLE_AMOUNT),
         REPORTING_DETECTION_LIMIT = as.numeric(REPORTING_DETECTION_LIMIT))
  
#same for qa table
qa_df2<-qa_df %>% 
  mutate(ANALYSIS_DATETIME = as.POSIXct(as.Date(ANALYSIS_DATETIME,"%Y-%m-%d"),
                                        tz = "America/New_York"),
         DILUTION_FACTOR = as.numeric(DILUTION_FACTOR),
         FINAL_VOLUME = as.numeric(FINAL_VOLUME),
         METHOD_DETECTION_LIMIT = as.numeric(METHOD_DETECTION_LIMIT),
         PREP_DATETIME = as.POSIXct(as.Date(PREP_DATETIME,"%m/%d/%Y"),
                                    tz = "America/New_York"),
         QUANTITATION_LIMIT = as.numeric(QUANTITATION_LIMIT),
         SUBSAMPLE_AMOUNT = as.numeric(SUBSAMPLE_AMOUNT),
         REPORTING_DETECTION_LIMIT = as.numeric(REPORTING_DETECTION_LIMIT))

#check it again

check<-janitor::compare_df_cols(result_df, 
                         result.all.formatted2, 
                         return = "mismatch")

#NOICE these are good

```

```{r check the sample table}

sample_df <- arrow::open_dataset(sources = file.path(build_dir, "SAMPLE.parquet")) |> 
  filter(SAMPLE_DELIVERY_GROUP %in% "R1603723") %>% #trying to limit it so the collection isnt crazy
  distinct() %>% 
  collect()

check<-janitor::compare_df_cols(sample_df, 
                         sample.all.formatted, 
                         return = "mismatch")

sample.all.formatted2<-sample.all.formatted %>% 
  mutate(REPLICATE = as.character(REPLICATE),
         SAMPLE_LATITUDE = as.numeric(SAMPLE_LATITUDE),
         SAMPLE_NAME = as.character(SAMPLE_NAME))

check<-janitor::compare_df_cols(sample_df, 
                         sample.all.formatted2, 
                         return = "mismatch")

#Heck ya it matches
```


```{r write files to RDS}

#combine sample and results table for the bacteria 

bacteria_final <-left_join(result.all.formatted2,
                       sample.all.formatted2,
                       by = c("EVENT_ID","SITE_ID")) # as of 1/6/25 advised to keep them separate

bacteria_final<-bacteria_final %>% 
  distinct()
#number of rows match! 376 in both

skimr::skim(bacteria_final)

```

```{r write these to RDS}

# saveRDS(
#   object = bacteria_final,
#   file = file.path(
#     "L:",
#     "DOW",
#     "BWAM Share",
#     "data",
#     "data_warehouse_staging",
#     "2024_V3",
#     "raw_data",
#     "bacteria_data_2024.rds"
#   )
# )


saveRDS(
  object = sample.all.formatted2,
  file = file.path(
    "L:",
    "DOW",
    "BWAM Share",
    "data",
    "data_warehouse_staging",
    "2024_V3",
    "raw_data",
    "bacteria_data_2024_sample.rds"
  )
)

saveRDS(
  object = result.all.formatted2,
  file = file.path(
    "L:",
    "DOW",
    "BWAM Share",
    "data",
    "data_warehouse_staging",
    "2024_V3",
    "raw_data",
    "bacteria_data_2024_results.rds"
  )
)

saveRDS(
  object = qa_df2,
  file = file.path(
    "L:",
    "DOW",
    "BWAM Share",
    "data",
    "data_warehouse_staging",
    "2024_V3",
    "raw_data",
    "bacteria_data_2024_qaqc_records.rds"
  )
)

```


